---
output: html_document
---

## [**Projects that the LabR Group is working on or has already completed**]{style="color:darkgreen"}

<br>

### [**PROJECT 1 -- Reference Interval Tool (LabRI Tool)**]{style="color:darkblue"}

```{r code1, echo=FALSE,warning=FALSE,message=FALSE}


library(htmltools)

# Definir o caminho para a imagem
image_path <- "https://i.imgur.com/1gduejq.png" 

# Criar um arquivo HTML que contém a imagem
html_file <- tempfile(fileext = ".html")
writeLines(paste0('<img src="', image_path, '" alt="Imagem" width="25%">'), html_file)

# Incluir o arquivo HTML no relatório
includeHTML(html_file)
```

<br>

::: {style="text-align: justify; text-indent: 30px; line-height: 1.8; color: black;"}
The "Laboratory Reference Interval" (**LabRI**) **method** employs a multi-criteria automated approach, integrating various algorithms throughout different stages to identify the optimal reference distribution (related to the reference subpopulation) and calculate reference limits (RLs). The pipeline sequentially arranges algorithms and each step's output is the next step's input. The method was developed through an analysis of publications on recommendations, limitations, and findings in biostatistics applied to laboratory results and RIs. It emphases data distribution analysis, outlier detection, mixture deconvolution, data transformation, and distribution truncation.
:::

**Example:**

<br>

```{r code2, echo=FALSE,warning=FALSE,message=FALSE}


library(htmltools)

# Definir o caminho para a imagem
image_path <- "https://i.imgur.com/QTws4An.jpg" 

# Criar um arquivo HTML que contém a imagem
html_file <- tempfile(fileext = ".html")
writeLines(paste0('<img src="', image_path, '" alt="Imagem" width="65%">'), html_file)

# Incluir o arquivo HTML no relatório
includeHTML(html_file)
```

<br>

```{r code3, echo=FALSE,warning=FALSE,message=FALSE}


library(htmltools)

# Definir o caminho para a imagem
image_path <- "https://i.imgur.com/sPZnrvo.jpg" 

# Criar um arquivo HTML que contém a imagem
html_file <- tempfile(fileext = ".html")
writeLines(paste0('<img src="', image_path, '" alt="Imagem" width="65%">'), html_file)

# Incluir o arquivo HTML no relatório
includeHTML(html_file)
```

<br>

<br>

<br>

<br>

<br>

<br>

<br>

<br>

<br>

<br>


